---
title: "Decision analysis of Rubber and Black pepper agroforestry in Nepal"
author: "[Norina], Peter Asare-Nuamah, Aditi Bista, Heidi Hoffmann, Kalu Onyinyechi, DOrcas Sanginga"
date: "`r Sys.Date()`"
output: bookdown::html_document2:
      theme: cerulean
      toc: true
      toc_float: true
      toc_depth: 2
      number_sections: true
      number_figures: true

bibliography: 
  - bib/references.bib 
  - bib/packages.bib

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(decisionSupport)
library(DiagrammeR)
```


# HowTo: Croff-References of Tables anf Figures
1. Copy the BibTex code of the reference into the bib/references textfile in the repository
2. insert the ```{asis, echo=FALSE}``` opton in in the r-chunk where you want to cite (see example below).
3. Citation: see example

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

For citing: Figure - \@ref(fig:name) , Table - \@ref(tab:table)

i.e. \@ref(tab:inputtable)


# HowTo: References 
In-text references: ```[@R-<shorturl as stated in the bibtex file>]``` i.e. The [@decisionSupport] package
was used to conduct the MC simulation as well as the NPV and VoI calcutations.


```{r, add_packages_bib, include=FALSE}
knitr::write_bib(c(.packages(),
                   'decisionSupport', 'DiagrammeR'), 'bib/packages.bib')

```


# Introduction

# Methods

## Input estimates

```{r input_table, caption= "Input variables as used in the decision analysis.", echo=FALSE, warning=FALSE}
library(knitr)
options(scipen = 999)

input_estimates <- read.csv("./data/AF_input_table.csv", header = TRUE, sep = ";")

input_estimates = subset(input_estimates, select = -c(median))
kable(input_estimates[2:7])
``` 

Since Black Pepper grows best within moist climate, it's cultivation usually requires irrigation. The climate of Eastern Nepal is marked by the annual Monsoon and long dry seasons during winter. Thereby, especially the wintermonths are crucial to archieve high yields and often, Pepper plants need to be irrigated. _[This knowledge was obtained by a fast literature research, Aditi and Team Report can you correct false facts if you humble over such? - Heidi]_ 
We assumed that growing Black Pepper next to Rubber trees could either mitigate irrigation requirements as the rubber's shadow would increase the moisture, or amplify them as the roots in the topsoil could compete for water and both crops would produce smaller harvests.

## Code

### Variating variables
Every variable calculated with vv() function.

### Chance events
Every variable calulated with chance_event().

### Model function, NPV and EVPI calculation

```{r, echo=T, warning=F}
library(decisionSupport)

# Read data----
table <- read.csv("./data/AF_input_table.csv", sep = ";")
str(table) # check whether reading data was successful


# Model function----

model_function <- function() {

  ##Natural benefits ----
  ##enhanced nutrient cycle
  mono_nutrient <- vv(var_mean = mono_nutrient,
                            var_CV = var_mono_nutrient,
                            n = n_years) * mono_nutrient_saved
  mono_nutrient_saved <- mono_nutrient
  
  AF_nutrient <- vv(var_mean = AF_nutrient,
                            var_CV = var_AF_nutrient,
                            n = n_years)
  AF_nutrient_saved <- AF_nutrient * AF_nutrient_saved
  

  ## Yields----
  # Scenarios
  ### As it is not known yet, the moist microclimate underneath the rubber trees can result in higher 
  ### pepper yields or, on the other hand, competition of the roots might lead to lower yields of both crops
  water_competition <- chance_event(water_competition_probability, value_if = 1, value_if_not = 0)
  
  ### Account for risk in diminished yields due to knowledge gaps especially at the initial phase
  ### and risk of knowledge gaps that could also lead to lower yields
  management_errors <- vv(var_mean = knowledge_gap_probability, var_CV = var_knowledge_gap_probability,
                          n = n_years, relative_trend = - 10)
  
  # Yield incomes
  rubber_yield <- vv(var_mean = max_rubber_yield, var_CV = var_rubber_yield, n = n_years)
  rubber_yield <- rubber_yield * (1 - management_errors) * (1 - water_competition * yield_if_competition)
  rubber_income <- rubber_yield * rubber_price
    
  pepper_yield <- vv(var_mean = max_pepper_yield, var_CV = var_pepper_yield, n = n_years)
  pepper_yield <- pepper_yield * (1 - management_errors)* (1 - water_competition * yield_if_competition)
  pepper_income <- pepper_yield * pepper_price
  

  ## Summarize benefits
  rubber_benefit <- rubber_income + mono_nutrient_saved
  AF_benefit <- pepper_income + rubber_income + AF_nutrient_saved
  

  ## Costs----
  ### Establishment costs in 1rst year
  establistment_cost_mono <- c(establishment_cost_mono, rep(0, n_years))
  establistment_cost_AF <- c(establishment_cost_AF, rep(0, n_years))
  
  maintenance_cost_mono <- vv(var_mean = rubber_main_cost, var_CV = var_rubber_main_cost,
                              n = n_years)
  maintenance_cost_pepper <- vv(var_mean = pepper_main_cost, var_CV = var_pepper_main_cost,
                              n = n_years)
  
  
  ### Water costs
  ### pepper needs to be irrigated which is an addition cost.
  price_water <- vv(cost_water, var_cost_water, n_years)
  
  if (water_competition) {
    AF_water <- vv(mean_AF_water, var_AF_water, n_years)
  } else {
    AF_water <- vv(competition_AF_water, var_AF_water, n_years)
  }
    
  cost_AF_water <- AF_water * price_water
  
  
  ## Substracting the costs to get final benefits----
  final_income_mono <- rubber_benefit - (maintenance_cost_mono + establishment_cost_mono)
    
  ### AF
  final_income_AF <- AF_benefit + rubber_benefit - (establishment_cost_AF + maintenance_cost_pepper
                                                   + maintenance_cost_mono + cost_AF_water)

  ### discount rate
  NPV_mono <- discount(final_income_mono, discount_rate = 10, calculate_NPV = TRUE)
  NPV_AF <- discount(final_income_AF, discount_rate = 10, calculate_NPV = TRUE)
  
  ## Overall NPV of the decision ----
  NPV_decision <- NPV_AF - NPV_mono
  
  return(list(NPV_mono =  NPV_mono,
              NPV_AF =  NPV_AF, 
              NPV_decision = NPV_decision))
  
  }


# Montecarlo Simulation----
AF_mc_simulation <- mcSimulation(as.estimate(table),
                                         model_function = model_function,
                                         numberOfModelRuns = 200,
                                         functionSyntax = "plainNames")
write.csv(AF_mc_simulation, "./results/1_MC_simulation_reuslts.csv")

# VoI ----
mcSimulation_table <- data.frame(AF_mc_simulation$x, 
                                      AF_mc_simulation$y[3])
mcSimulation_table

AF_evpi <- multi_EVPI(mc = mcSimulation_table, 
                        first_out_var = "NPV_decision")
AF_evpi
write.csv(AF_evpi, "./results/2_evpi_results.csv")

```

# Results and discussion

## Net Present Value (NPV) distributions

```{r NPVs, echo=F, fig.align='center', fig.cap="Difference in NPV between Agroforestry system and Rubber monoculture."}
plot_distributions(mcSimulation_object = AF_mc_simulation,
                   vars = c("NPV_mono" , "NPV_AF"),
                   method = 'smooth_simple_overlay',
                   base_size= 11)

```


## Value of Information (VoI) analysis

```{r VoI, echo=F, fig.align='center', fig.cap="Results of the Value of Information analysis."}

#if you want to reference to this fig, use \@ref(fig:VoI)

plot_evpi(AF_evpi, decision_vars = "NPV_decision")
```


## Cashflow??



