---
title: "Improving smallholder revenue through intercropping rubber and black pepper: A case study of Nepal"
author: "Norina Murtaza, Peter Asare-Nuamah, Aditi Bista, Heidi Hoffmann, Kalu Onyinyechi, Dorcas Sanginga"
date: "2023-07-03"
output: bookdown::html_document2:
      theme: cerulean
      toc: true
      toc_float: true
      toc_depth: 2
      number_sections: true
      number_figures: true

bibliography: 
  - bib/references.bib 
  - bib/packages.bib

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(decisionSupport)
library(DiagrammeR)
```


# HowTo: Croff-References of Tables and Figures
1. Copy the BibTex code of the reference into the bib/references textfile in the repository
2. insert the ```{asis, echo=FALSE}``` option in the r-chunk where you want to cite (see example below).
3. Citation: see example

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

For citing: Figure - \@ref(fig:name) , Table - \@ref(tab:table)

i.e. \@ref(tab:input table)


# HowTo: References 
In-text references: ```[@R-<shorturl as stated in the bibtex file>]``` i.e. The [@decisionSupport] package
was used to conduct the MC simulation as well as the NPV and VoI calcutations.


```{r, add_packages_bib, include=FALSE}
knitr::write_bib(c(.packages(),
                   'decisionSupport', 'DiagrammeR'), 'bib/packages.bib')

```


# Introduction
Natural rubber is a significant agricultural product that is utilized in the production of a variety of products (Fox & Castella, 2013). In Nepal, rubber agroforestry, has emerged a new sustainable agricultural approach which combines the development of rubber with the integration of several tree species. The combination of rubber trees with other beneficial tree species helps to improve the ecological and financial advantages of rubber farming. Due to its potential to alleviate environmental degradation, enhance rural livelihoods, and advance climate change mitigation and adaptation, this agroforestry system has attracted attention recently.
Intercropping of black pepper and rubber in Nepal capitalizes on their complementary growth patterns. Black pepper, a vine-like plant, thrives in the shade provided by the rubber trees, utilizing the vertical space and reducing weed competition. While, the rubber trees benefit from the protection provided by the pepper vines, which act as a natural windbreak and provide a microclimate conducive to rubber growth. Nepal, being a country known for its diverse agro-climatic conditions, offers a favorable environment for intercropping of rubber with Black pepper. Black pepper (Piper nigrum) is a high-value spice crop, while rubber (Hevea brasiliensis) is a profitable cash crop. By integrating these two crops in a well-planned agroforestry system, farmers in Nepal will be able to maximize their productivity and economic returns.

# Current Situation of Rubber Production in Nepal
Nepal's climate and land slope make natural rubber cultivation ideal for addressing issues such as underemployment, underutilization of land, and poverty. However, rubber monocropping poses several challenges for farmers, including a lack of income during the long immature period, vulnerability to price shocks, seasonality, disease outbreaks, and natural disaster (DERAF report, 2020). There is a high level of rubber and pepper imports because of tight supply conditions in Nepal (Economic times, 2020). To overcome these obstacles there is a need to promoting rubber agroforestry practices especially with compatible and mutual beneficial crop species. 

# Why Rubber and Black Pepper Agroforestry system
Integrating black pepper and Rubber in an agroforestry system can offer a solution to improve food security, increase farmers' income, and enhance their livelihoods (Rahman et al., 2012). Intercropping rubber with black pepper enables smallholders to diversify their income sources and optimize land utilization during the initial six years it takes for rubber trees to become productive (Pepper Hub). Additionally, shading black pepper with rubber trees creates favorable growth conditions, including decreased irradiance and temperature, increased relative humidity, and higher leaf expansion, demonstrating adaptation to low light (Oleosio et al., 2021).

# Decision Problem
To improve income and the livelihoods of farmers in Nepal farmers might want to adopt rubber agroforestry practices, specifically integrating black pepper cultivation with rubber, as an alternative to rubber monocropping.  Farmers decisions are influenced by factors such as;
1. Economic Impact: These assess the potential income generation and economic viability of rubber agroforestry practices compared to rubber monocropping, considering factors such as yield, market demand, price stability, and income diversification opportunities. 
2. Risk and Resilience: focuses on assessing the vulnerability of rubber agroforestry practices to price shocks, disease outbreaks, natural disasters, and other risks, while identifying strategies to mitigate them. 
3. Policy and Market Support: Involves the evaluation of existing policies, incentives, and market linkages to facilitate the adoption of rubber agroforestry practices, addressing any barriers and gaps. 
4. Cost-Benefit Analysis: This focuses on a comprehensive cost-benefit analysis, comparing the economic, environmental, and social benefits of rubber agroforestry practices with rubber monocropping.
5. Technical knowledge and support: This considers whether farmers have access to technical knowledge and support. This includes understanding the agronomic practices, pest and disease management, harvesting, processing, and marketing strategies for both crops. Training programs, extension services, and collaboration with agricultural experts can help address these knowledge gaps.

# Decision Maker
The decision makers for this project are the smallholder rubber farmers in Nepal. The ultimate goal is to improve their income and livelihoods.

# Decision Alternatives
1. Alternative 1: Promote Rubber Monocropping 
2. Alternative 2: Promote Rubber and Black Pepper Agroforestry 

# Methods
## Conceptual model
A conceptual model which the influence of rubber and black pepper Agroforestry cost and benefits on Net Present value (NPV) was developed. The total cost comprised of establishment cost and maintenance cost, while total benefits comprised of Natural and Financial benefit. Lack of technical knowledge, Economic fluctuation and ownership of land were the major risk identified. A discount rate of 10% was chosen to calculate the Net present Value.

## Input estimates

```{r input_table, caption= "Input variables as used in the decision analysis.", echo=FALSE, warning=FALSE}
library(knitr)
options(scipen = 999)

input_estimates <- read.csv("./data/AF_input_table.csv", header = TRUE, sep = ";")

input_estimates = subset(input_estimates, select = -c(median))
kable(input_estimates[2:7])
``` 

Since Black Pepper grows best within moist climate, its cultivation usually requires irrigation. The climate of Eastern Nepal is marked by the annual Monsoon and long dry seasons during winter. Thereby, especially the winter months are crucial to achieve high yields, and often, Pepper plants need to be irrigated. _[This knowledge was obtained by a fast literature research, Aditi and Team Report can you correct false facts if you humble over such? - Heidi]_ 
We assumed that growing Black Pepper next to Rubber trees could either mitigate irrigation requirements as the rubber's shadow would increase the moisture, or amplify them as the roots in the topsoil could compete for water and both crops would produce smaller harvests.
Additionally, it is reported that litterfall releases high amounts of primary macronutrients such as Nitrogen, Phosphorous, and potassium (NPK) back into the soil. Estimating how much each system recycles will help to determine the profitability and sustainability of the studied systems in regard to nutrient cycling and minimize fertilization inputs in the following cropping systems.

## Code

### Variating variables
Every variable calculated with vv() function.

### Chance events
Every variable calulated with chance_event().

### Model function, NPV and EVPI calculation

```{r, echo=T, warning=F}
library(decisionSupport)

# Read data----
table <- read.csv("./data/AF_input_table.csv", sep = ";")
str(table) # check whether reading data was successful


# Model function----

model_function <- function() {

  ##Natural benefits ----
  ##Nutrient accession (from litterfall)

mono_nutrient <- vv(var_mean = mono_nutrient,
                            var_CV = var_mono_nutrient,
                            n = n_years) 

mono_nutrient_saved <- mono_nutrient* fertilizer_price  #Monetary value of NPK fertilizer bags saved in rubber monoculture

AF_nutrient <- vv(var_mean = AF_nutrient,
                            var_CV = var_AF_nutrient,
                            n = n_years)

AF_nutrient_saved <- AF_nutrient * fertilizer_price  #Monetary value of NPK fertilizer bags saved in rubber and pepper system  


  ## Yields----
  # Scenarios
  ### As it is not known yet, the moist microclimate underneath the rubber trees can result in higher 
  ### pepper yields or, on the other hand, competition of the roots might lead to lower yields of both crops
  water_competition <- chance_event(water_competition_probability, value_if = 1, value_if_not = 0)
  
  ### Account for risk in diminished yields due to knowledge gaps especially at the initial phase
  ### and risk of knowledge gaps that could also lead to lower yields
  management_errors <- vv(var_mean = knowledge_gap_probability, var_CV = var_knowledge_gap_probability,
                          n = n_years, relative_trend = - 10)
  
  # Yield incomes
  rubber_yield <- vv(var_mean = max_rubber_yield, var_CV = var_rubber_yield, n = n_years)
  rubber_yield <- rubber_yield * (1 - management_errors) * (1 - water_competition * yield_if_competition)
  rubber_income <- rubber_yield * rubber_price
    
  pepper_yield <- vv(var_mean = max_pepper_yield, var_CV = var_pepper_yield, n = n_years)
  pepper_yield <- pepper_yield * (1 - management_errors)* (1 - water_competition * yield_if_competition)
  pepper_income <- pepper_yield * pepper_price
  

  ## Summarize benefits
  rubber_benefit <- rubber_income + mono_nutrient_saved
  AF_benefit <- pepper_income + rubber_income + AF_nutrient_saved
  

  ## Costs----
  ### Establishment costs in 1rst year
  establistment_cost_mono <- c(establishment_cost_mono, rep(0, n_years))
  establistment_cost_AF <- c(establishment_cost_AF, rep(0, n_years))
  
  maintenance_cost_mono <- vv(var_mean = rubber_main_cost, var_CV = var_rubber_main_cost,
                              n = n_years)
  maintenance_cost_pepper <- vv(var_mean = pepper_main_cost, var_CV = var_pepper_main_cost,
                              n = n_years)
  
  
  ### Water costs
  ### pepper needs to be irrigated which is an addition cost.
  price_water <- vv(cost_water, var_cost_water, n_years)
  
  if (water_competition) {
    AF_water <- vv(mean_AF_water, var_AF_water, n_years)
  } else {
    AF_water <- vv(competition_AF_water, var_AF_water, n_years)
  }
    
  cost_AF_water <- AF_water * price_water
  
  
  ## Substracting the costs to get final benefits----
  final_income_mono <- rubber_benefit - (maintenance_cost_mono + establishment_cost_mono)
    
  ### AF
  final_income_AF <- AF_benefit + rubber_benefit - (establishment_cost_AF + maintenance_cost_pepper
                                                   + maintenance_cost_mono + cost_AF_water)

  ### discount rate
  NPV_mono <- discount(final_income_mono, discount_rate = 10, calculate_NPV = TRUE)
  NPV_AF <- discount(final_income_AF, discount_rate = 10, calculate_NPV = TRUE)
  
  ## Overall NPV of the decision ----
  NPV_decision <- NPV_AF - NPV_mono
  
  return(list(NPV_mono =  NPV_mono,
              NPV_AF =  NPV_AF, 
              NPV_decision = NPV_decision))
  
  }


# Montecarlo Simulation----
AF_mc_simulation <- mcSimulation(as.estimate(table),
                                         model_function = model_function,
                                         numberOfModelRuns = 200,
                                         functionSyntax = "plainNames")
write.csv(AF_mc_simulation, "./results/1_MC_simulation_reuslts.csv")

# VoI ----
mcSimulation_table <- data.frame(AF_mc_simulation$x, 
                                      AF_mc_simulation$y[3])
mcSimulation_table

AF_evpi <- multi_EVPI(mc = mcSimulation_table, 
                        first_out_var = "NPV_decision")
AF_evpi
write.csv(AF_evpi, "./results/2_evpi_results.csv")

```

# Results and discussion

## Net Present Value (NPV) distributions

```{r NPVs, echo=F, fig.align='center', fig.cap="Difference in NPV between Agroforestry system and Rubber monoculture."}
plot_distributions(mcSimulation_object = AF_mc_simulation,
                   vars = c("NPV_mono" , "NPV_AF"),
                   method = 'smooth_simple_overlay',
                   base_size= 11)

```


## Value of Information (VoI) analysis

```{r VoI, echo=F, fig.align='center', fig.cap="Results of the Value of Information analysis."}

#if you want to reference to this fig, use \@ref(fig:VoI)

plot_evpi(AF_evpi, decision_vars = "NPV_decision")
```

# Uncertainties and Issues

# Conclusion



